Modelling BCG vaccination in the UK

### 2019-07-11 rmds/02-background.Rmd
packrat update

```{r tab-interventions, echo = FALSE, message = FALSE, dpi = 500}
tb_interventions_timeline %>% 
  set_names(c("Year",
              "Intervention",
              "Type",
              "Line",
              "Detail")) %>% 
  knitr::kable(
    caption.short = "A timeline of interventions against TB",
    caption = "A timeline of interventions against TB. Antibiotics used to treat TB are commonly given together, with those with the fewest side effects given first. Second line antibiotics are then used if the initial treatment fails or tests show the strain is multiply drug resistant. BCG - Bacillus Calmette–Guérin; TB – Tuberculosis; MRSA - Methicillin-resistant *Staphylococcus aureus*; DOTS - Directly Observed Treatment Short-course", booktabs = TRUE, longtable = TRUE, escape = FALSE) %>% 
  kable_styling(font_size = 8, latex_options = c("repeat_header")) %>% 
  column_spec(5, width = "10cm") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  landscape()
```

@@

```{r map-global-tb, fig.cap = "Global map of country level TB incidence rates (per 100,000 population) in 2017. Note the clustering of countries with high incidence rates in southern and central Africa and southern Asia. Incidence rates in the legend refer to the lower bound for each colour. Map produced using getTBinR", fig.scap = "Global map of country level TB incidence rates (per 100,000 population) in 201", fig.height = 6}
map_tb_burden(verbose = FALSE)
```

@@

```{r map-global-tb-with-hiv, fig.scap = "Global map of estimated HIV in incidence TB (percent) in 2017.", fig.cap = "Global map of estimated HIV in incidence TB (percent) in 2017. Note the high percentage of TB cases with HIV in sub-saharan Africa. The percentages of HIV in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR", fig.height = 6}
map_tb_burden(metric = "e_tbhiv_prct", verbose = FALSE)
```

@@

```{r map-global-tb-with-rr, fig.scap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017.", fig.cap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017. Note that a far higher percentage of TB cases have rifampicin resistance in the former Soviet Union that in the rest of the world. The percentages of rifampicin resistances in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR (see \\@ref(getTBinR) for details)", fig.height = 6}
map_tb_burden(metric = "e_rr_pct_new", verbose = FALSE)
```

@@

TB incidence in England and Wales has decreased dramatically from a century ago (Figure \@ref(fig:plot-incidence)^[or see [http://www.seabbs.co.uk/shiny/TB_England_Wales](http://www.seabbs.co.uk/shiny/TB_England_Wales]) for an interactive dashboard). However, in the past several decades, incidence rates first stabilised and have since increased since their lowest point in the 1990s. In 2000, there were 6044 notified TB cases in England, increasing to a maximum of 8280 notified TB cases in 2011. Since then, notifications have declined year on year.[@PHE2016a] Figure \@ref(fig:plot-incidence) includes the interventions discussed above (Table \@ref(tab:tab-interventions)) and indicates that the introduction of several antibiotics and BCG vaccination in the 1950s may have led to an extended decrease in incidence.

>>>>

```{r tab-interventions, echo = FALSE, message = FALSE, dpi = 500}
tb_interventions_timeline %>% 
  set_names(c("Year",
              "Intervention",
              "Type",
              "Line",
              "Detail")) %>% 
  knitr::kable(
    caption.short = "A timeline of interventions against TB",
    caption = "A timeline of interventions against TB. Antibiotics used to treat TB are commonly given together, with those with the fewest side effects given first. Second line antibiotics are then used if the initial treatment fails or tests show the strain is multiply drug resistant. BCG - Bacillus Calmette–Guérin; TB – Tuberculosis; MRSA - Methicillin-resistant \textit{Staphylococcus aureus}; DOTS - Directly Observed Treatment Short-course", booktabs = TRUE, longtable = TRUE, escape = FALSE) %>% 
  kable_styling(font_size = 8, latex_options = c("repeat_header")) %>% 
  column_spec(5, width = "10cm") %>% 
  kable_styling(latex_options = "hold_position") %>% 
  landscape()
```

@@

```{r map-global-tb, fig.cap = "Global map of country level TB incidence rates (per 100,000 population) in 2017. Note the clustering of countries with high incidence rates in southern and central Africa and southern Asia. Incidence rates in the legend refer to the lower bound for each colour. Map produced using getTBinR", fig.scap = "Global map of country level TB incidence rates (per 100,000 population) in 201"}
map_tb_burden(verbose = FALSE)
```

@@

```{r map-global-tb-with-hiv, fig.scap = "Global map of estimated HIV in incidence TB (percent) in 2017.", fig.cap = "Global map of estimated HIV in incidence TB (percent) in 2017. Note the high percentage of TB cases with HIV in sub-saharan Africa. The percentages of HIV in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR"}
map_tb_burden(metric = "e_tbhiv_prct", verbose = FALSE)
```

@@

```{r map-global-tb-with-rr, fig.scap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017.", fig.cap = "Global map of the estimated percentage of new TB cases with rifampicin resistance (percent) in 2017. Note that a far higher percentage of TB cases have rifampicin resistance in the former Soviet Union that in the rest of the world. The percentages of rifampicin resistances in incident TB in the legend refer to the lower bound for each colour. Map produced using getTBinR (see \\@ref(getTBinR) for details)"}
map_tb_burden(metric = "e_rr_pct_new", verbose = FALSE)
```

@@

TB incidence in England and Wales has decreased dramatically from a century ago (Figure \@ref(fig:plot-incidence)^[or see http://www.seabbs.co.uk/shiny/TB_England_Wales]) for an interactive dashboard). However, in the past several decades, incidence rates first stabilised and have since increased since their lowest point in the 1990s. In 2000, there were 6044 notified TB cases in England, increasing to a maximum of 8280 notified TB cases in 2011. Since then, notifications have declined year on year.[@PHE2016a] Figure \@ref(fig:plot-incidence) includes the interventions discussed above (Table \@ref(tab:tab-interventions)) and indicates that the introduction of several antibiotics and BCG vaccination in the 1950s may have led to an extended decrease in incidence.
